Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-04-15 manuscript/manuscript.Rmd
adds new posterior climate effect densities figure

>>>>

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/lppds_suppfig.png}
  \caption{Cross validation scores (summed log pointwise predictive density) plotted against the prior variance for $\boldsymbol{\beta}_C$. The optimal score for prediction for each species-vital rate combination is shown with a vertical red line.}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{./components/climate_posteriors_figure.png}
  \caption{Posterior distributions of climate effects ($\boldsymbol{\beta}_C$) for each species and vital rate statistical model. Since our priors were constrained via ridge-regression, we highlight climate effects whose 80\% credible intervals do not overlap zero (red for negative coefficients, blue for positive coefficients).}
\end{figure}
